---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# prg

<!-- badges: start -->
<!-- badges: end -->

The goal of prg is to ...

## Installation

You can install the released version of prgdownloader from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("prgdownloader")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("skowronskij/prg")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(prgdownloader)
poland_provinces = get_province()
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(poland_provinces$geometry)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
